Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Workshop Using Cutting-Edge Tools

### 2021-01-12 paper_contents.tex
Fix typos

\subsection{Part 4: Feedback and Closure}
After the demonstration and practice session for R Markdown, we will reconvene as a whole group to solicit feedback from the group on the two tools included in the Tutorial. As the tools are indended to be a useful resource to the ISLS community we hope to continually improve them over time, and will benefit from the perspective of new users. We will then take time to wrap up the session and give additional help or advice going forward. We will conclude by asking participants to sign up for reminder and update emails for either tool, and share out plan to reach out near the next ISLS deadline to support using the tools. The feedback and closure portion of the tutorial will take 20 minutes.

>>>>

\subsection{Part 4: Feedback and Closure}
After the demonstration and practice session for R Markdown, we will reconvene as a whole group to solicit feedback from the group on the two tools included in the Tutorial. As the tools are intended to be a useful resource to the ISLS community, we hope to continually improve them over time, and will benefit from the perspective of new users. We will then take time to wrap up the session and give additional help or advice going forward. We will conclude by asking participants to sign up for reminder and update emails for either tool, and share out plan to reach out near the next ISLS deadline to support using the tools. The feedback and closure portion of the tutorial will take 20 minutes.
